Probabilistic Forecasting of the Disturbance Storm Time Index: An Autoregressive Gaussian Process approach

### 2017-05-30 response-reviewer1.tex

\documentclass{article}
\begin{document}

\title{Response Reviewer 1}
\maketitle

\section*{Draft Comments \& Revisions}

\begin{enumerate}
\item{
  \fbox{%
    \parbox{\textwidth}{%
line 31: Dst: A continuous hourly index which gives a measure of the weakening or strengthening of the Earth's equatorial magnetic field due to the weakening or strengthening of the ring currents and the geomagnetic storms. \\
line 204: Dst gives a measure of ring currents. 
\\
\textbf{Comment}: Authors should add that ring current is not the only current that contributes to the Dst evolution. 
The authors should mention the contribution of near -Earth cross-tail current (e.g. Ganushkina, et al., Ann. Geophys. 22, 1317-1334, 2004; Ganushkina, et al.. Ann. Geophys. 28, 123- 140, 2010); partial ring current 
(e.g. Liemohn et al. J. Geophys. Res. 106, 10883-10904, 2001), substorm current wedge (e.g. Munsami, J. Geophys. Res. 105(A12), 27833-27840, 2000); magnetopause current. }
}

\textbf{Response}: Changes made in lines 32-36 in the file \texttt{changes.pdf}

}

\item{

\fbox{%
\parbox{\textwidth}{%
line 52-53: "The NARMAX methodology builds models by constructing polynomial expansions of inputs and determines the best combinations of monomials to include in the refined model by using a criterion called the error reduction ratio (ERR)."

\textbf{Comment}: NARMAX similar to NARX modelling is not limited to the polynomial based approach. It could employ wide range of sets of functions that form basis e.g. radial basis functions, wavelets etc. (e.g.: Wei et al., Wavelet based non-parametric NARX models for nonlinear input-output system identification; International Journal of Systems Science, Volume: 37, Issue: 15, Pages: 1089-1096, DOI: 10.1080/00207720600903011, Published: DEC 15 2006; Wei et al., Prediction of the Dst index using multiresolution wavelet models; JGR-SP, 109, A7, DOI: 10.1029/2003JA010332, 2004). Please modify the statement about NARMAX.

}
}

\textbf{Response}: Changes made in lines 59-62 in the file \texttt{changes.pdf}

}

\item{

\fbox{%
\parbox{\textwidth}{%
line 122: "Since we have noisy measurements of f over the training data, we add the noise variance σ2"

\textbf{Comment}: V and Bz are used in the current manuscript for GP-ARX model. It is well known that P dynamic pressure affects the Dst. Please discuss if the un-accounted inputs like P can affect statistical properties of "noise" and if these un-accounted inputs can affect the structure of the model.

}
}

\textbf{Response}: Revisions made in lines 239-249 in the file \texttt{changes.pdf}

}

\item{

\fbox{%
\parbox{\textwidth}{%
"Therefore, our exogenous parameters consist of solar wind velocity Vsw and IMF Bz."

\textbf{Comment}: There were many previously published papers that tried to identify the coupling functions between the solar wind and the Dst index. Since the introduction of Acasofu "epsilon" parameter many coupling functions include also "clock angle". Please explain in more detail why it was decided not to include "clock angle" into the set of parameters.

}
}

\textbf{Response}: Revisions made in lines 239-249 in the file \texttt{changes.pdf}

}

\item{

\fbox{%
\parbox{\textwidth}{%
Line 219: "It is known that the so called persistence model Dˆ st(t) = Dst(t − 1) performs quite well in the context of OSA prediction"

\textbf{Comment}: I think the major aim of various Dst forecasting tools is to predict in advance sever geomagnetic storms. Persistence model will fail exactly at the moment when accurate prediction is required, one step before the initiation of major geomagnetic storms. If some statistical parameters show that the persistence model performs quite well, thats mean that these parameters are not adequate in the assessment of forecasting tools and some other parameters should be used. Please modify the phrase above.

}
}

\textbf{Response}: Revisions made in lines 268-270 and 340-347 in the file \texttt{changes.pdf}

}

\item{

\fbox{%
\parbox{\textwidth}{%

\textbf{Comment}: Figures 5,6,7. Please expand the time interval shown. The figure should include the reasonable period of quiet time before and after the geomagnetic storm.

}
}

\textbf{Response}: Changes made for the figures 5-7

}

\end{enumerate}

\end{document}

### 2017-05-31 response-reviewer1.tex

\documentclass{article}
\begin{document}

\title{Response Reviewer 1}
\maketitle

\section*{Draft Comments \& Revisions}

\begin{enumerate}

\fbox{%
    \parbox{\textwidth}{%
\textbf{Comment}: The authors state the proposed methodology allows to construct error bars on the predictions. I think this can not be considered as a significant advantage because the past-cast performance for any forecasting tool can be used to construct statistical error bars for the prediction.}
}

\textbf{Response}: Changes made in lines 91-97 in the file \texttt{changes.pdf}

\item{
  \fbox{%
    \parbox{\textwidth}{%
line 31: Dst: A continuous hourly index which gives a measure of the weakening or strengthening of the Earth's equatorial magnetic field due to the weakening or strengthening of the ring currents and the geomagnetic storms. \\
line 204: Dst gives a measure of ring currents. 
\\
\textbf{Comment}: Authors should add that ring current is not the only current that contributes to the Dst evolution. 
The authors should mention the contribution of near -Earth cross-tail current (e.g. Ganushkina, et al., Ann. Geophys. 22, 1317-1334, 2004; Ganushkina, et al.. Ann. Geophys. 28, 123- 140, 2010); partial ring current 
(e.g. Liemohn et al. J. Geophys. Res. 106, 10883-10904, 2001), substorm current wedge (e.g. Munsami, J. Geophys. Res. 105(A12), 27833-27840, 2000); magnetopause current. }
}

@@

\fbox{%
\parbox{\textwidth}{%
line 122: "Since we have noisy measurements of f over the training data, we add the noise variance σ2"

\textbf{Comment}: V and Bz are used in the current manuscript for GP-ARX model. It is well known that P dynamic pressure affects the Dst. Please discuss if the un-accounted inputs like P can affect statistical properties of "noise" and if these un-accounted inputs can affect the structure of the model.

}
}

\textbf{Response}: Revisions made in lines 229-233, 243-253 and 256-265 in the file \texttt{changes.pdf}

@@

\fbox{%
\parbox{\textwidth}{%
"Therefore, our exogenous parameters consist of solar wind velocity Vsw and IMF Bz."

\textbf{Comment}: There were many previously published papers that tried to identify the coupling functions between the solar wind and the Dst index. Since the introduction of Acasofu "epsilon" parameter many coupling functions include also "clock angle". Please explain in more detail why it was decided not to include "clock angle" into the set of parameters.

}
}

\textbf{Response}: Revisions made in lines 243-253 in the file \texttt{changes.pdf}

@@

\fbox{%
\parbox{\textwidth}{%
Line 219: "It is known that the so called persistence model Dˆ st(t) = Dst(t − 1) performs quite well in the context of OSA prediction"

\textbf{Comment}: I think the major aim of various Dst forecasting tools is to predict in advance sever geomagnetic storms. Persistence model will fail exactly at the moment when accurate prediction is required, one step before the initiation of major geomagnetic storms. If some statistical parameters show that the persistence model performs quite well, thats mean that these parameters are not adequate in the assessment of forecasting tools and some other parameters should be used. Please modify the phrase above.

}
}

\textbf{Response}: Revisions made in lines 272-273 and 344-351 in the file \texttt{changes.pdf}

### 2017-05-31 response-reviewer2.tex

\documentclass{article}
\begin{document}

\title{Response Reviewer 2}
\maketitle

\section*{Draft Comments \& Revisions}

\begin{enumerate}

\item{

\fbox{%
    \parbox{\textwidth}{%
\textbf{Comment}:

The authors must be care to review completely the researches from classical to intelligent methods for prediction of Dst, Kp. For example some of references are missing is: 
(a)- Javad Sharifie, Caro Lucas, and Babak N. Araabi, "Locally linear neurofuzzy modeling and prediction 
of geomagnetic disturbances based on solar wind conditions", Space Weather, Vol 4, 2006 
(b)- Javad Sharifi, Babak N. Araabi, and Caro Lucas, "Multi-step prediction of Dst index using singular spectrum analysis and locally linear neurofuzzy modeling", Earth Planets Space, 58, 331-341, 2006 
(c)- Loskutov, A., I. A. Istomin, K. M. Kuzanyan, and O. L. Kotlyarov, Testing and forecasting the time series of the solar activity by singular spectrum analysis, Nonlin. Phenomena in Complex Syst., 4(1), 47-57, 2001a. 
(d)- Loskutov, A., I. Istomin, O. Kotlyarov, and K. Kuzanyan, A study of the regularities in Solar magnetic activity by singular spectrum analysis, Astronomy Letters, 27(11), 745-753, 2001b 
And some of other which especially used for Dst predition from one step to multi-step.

}
}

\textbf{Response}: Revisions made in lines 74-85 in the file \texttt{changes.pdf}

}

\item{

\fbox{%
    \parbox{\textwidth}{%
\textbf{Comment}: To select best number of time lags of input regressor vector, you must use structure identification. To do this, an error criteria must be obtain based on number of time lags of each physical component. The error criteria has a minimum which is appropriate number of lagged time series.

}
}

\textbf{Response}: In section 4, we have specified that the model lags for each input component are chosen based on the predictive performance of each generated model on the validation data set. The storm events which comprise the validation data set are specified in table 4 of the manuscript. It is based on this method that we choose the time lags for each input. Care has been taken that no events of the validation data set overlap with the training or test data to ensure unbiased model lag selection.

}

\item{

\fbox{%
    \parbox{\textwidth}{%
\textbf{Comment}: In this paper, even for one step, has one-step time delay, which means that prediction is near Markov (The last observed data is the prediction of next time step), it is obvious from figures 5-7. Then the prediction results is useless. To enhance this, some corrections is in front of authors: they may correct the method to non-Markovian OSA, or use the hybrid prediction methods for example combination of spectrum analysis with OSA or any other hybrid methods.

}
}

\textbf{Response}: The GP-AR and GP-ARX models are strictly speaking non-Markovian models which we have explained in lines 274-281 in the file \texttt{changes.pdf}. Although many predictive models for $Dst$ are non-Markovian in formulation, due to strong \emph{persistence} behavior in the OMNI data, the Markovian component is always a dominant portion of all $Dst$ predictions.

This can be observed in figures 7, 9 in Javad Sharifi, Babak N. Araabi, and Caro Lucas, "Multi-step prediction of Dst index using singular spectrum analysis and locally linear neurofuzzy modeling", Earth Planets Space, 58, 331-341, 2006.

The NARMAX Dst OSA model as outlined in equation 2 of R. J. Boynton, M. A. Balikhin, S. A. Billings, A. S. Sharma, and O. A. Amariutei, "Data derived NARMAX Dst model", has a strong persistence/Markovian component ($0.8335 Dst(t-1)$) which is more significant as compared to the other terms of the model expansion.

We, the authors argue that this is an artifact of the OMNI data and not inductive bias of the $Dst$ models in question.

}

\item{

\fbox{%
    \parbox{\textwidth}{%
\textbf{Comment}: For enhanced method which author must develop, several extreme geomagnetic storms must be used to validate the method. In this storms the Dst index must be below of -300nT, i.e. Dst < -300nT for example extreme geomagnetic storm of 1989 (Dst goes to about -600nT) and etc. in this way, the author can postulate that have contribution for geomagnetic storm prediction.
}
}

\textbf{Response}: With respect to the storm of 1989, there is very little solar wind $V$ and IMF $B_z$ data available for that particular event, hence it was not possible to calculate predictions for it. The authors would however, like to bring to attention event numbers 16 and 43 in table 5 of the manuscript. These events are a part of the test set used to evaluate the GP-AR and GP-ARX models. We have shown predictions for both in tables 6 and 7 of the revised manuscript.

}

\end{enumerate}
\end{document}

### 2017-05-31 revised-draft.tex
Response Reviewers added

%Local neurofuzzy modelling and singular spectrum analysis.
Apart from the NARMAX and neural network approaches, fuzzy methods have also been applied for $Dst$ prediction, \citet{SWE:SWE146} and \citet{Sharifi2006} outline the application of \emph{Local Neurofuzzy} models for one hour and two hour predictions of $Dst$ respectively. Local neuro-fuzzy models reduce the input space into a number of regions each with its own expert predictor. The combined model predicts $Dst$ for a new point as a linear combinations of the predictions from each expert weighted by a fuzzy score signifying the importance of each model for the provided input. For improving predictive performance of two hour $Dst$ forecasts the authors use \emph{singular spectrum analysis} SSA \citet{loskutov2001testing}, \citet{loskutov2001study}.

%Talk about need for probabilistic forecasts.
Although much research has been done on prediction of the $Dst$ index, much less has been done on probabilistic forecasting of $Dst$. One such work described in \citet{McPherron:2013} involves identification of high speed solar wind streams using the WSA model (see \citet{WSAModel}), using predictions of high speed streams to construct ensembles of $Dst$ trajectories which yield the quartiles of $Dst$ time series. A simple way to construct error bars on the predictions of forecasting models is by using the so called \textit{past cast} performance i.e. by calculating the standard deviations of the predictions generated by the model on a hold out data set. One limitation of such an approach is that the variance of the model predictions, once computed, remains static and does not adapt according to the inputs provided to the model. This may lead to overestimation or underestimation of the uncertainty around a models predictions depending on the prevelant geo-magnetic conditions and the data set used to calculate the \textit{past cast} model performance.

@@

From the validation results, we can chose the model order which yields the best performance, for GP-AR it is $p_t = 6$ while for GP-ARX it is $p_t = 11$. Further examination of the validation results shows that in the scheme $p_t = 11$ choosing $p = 6, p_v = 1, p_b = 3$ gives superior results.

@@

\begin{table}[h]
\fontsize{9}{10.4}\selectfont
\centering
\caption{Storm events used to evaluate GP-AR and GP-ARX models}
\label{table:teststorms}
\begin{tabular}{cccccc}
\hline
Event Id & Start Date & Start Time & End Date & End Time & min. Dst \\ \hline
1 & 1998/02/17 & 1200 & 1998/02/18 & 1000 & -100 \\
2 & 1998/03/10 & 1100 & 1998/03/11 & 1800 & -116 \\
3 & 1998/05/04 & 0200 & 1998/05/05 & 0200 & -205 \\
4 & 1998/08/26 & 1000 & 1998/08/29 & 0700 & -155 \\
5 & 1998/09/25 & 0100 & 1998/09/26 & 0000 & -207 \\
6 & 1998/10/19 & 0500 & 1998/10/20 & 0800 & -112 \\
7 & 1998/11/09 & 0300 & 1998/11/10 & 1600 & -142 \\
8 & 1998/11/13 & 0000 & 1998/11/15 & 0400 & -131 \\
9 & 1999/01/13 & 1600 & 1999/01/14 & 2000 & -112 \\
10 & 1999/02/18 & 0300 & 1999/02/19 & 2100 & -123 \\
11 & 1999/09/22 & 2000 & 1999/09/23 & 2300 & -173 \\
12 & 1999/10/22 & 0000 & 1999/10/23 & 1400 & -237 \\
13 & 2000/02/12 & 0500 & 2000/02/13 & 1500 & -133 \\
14 & 2000/04/06 & 1700 & 2000/04/08 & 0900 & -288 \\
15 & 2000/05/24 & 0100 & 2000/05/25 & 2000 & -147 \\
16 & 2000/08/10 & 2000 & 2000/08/11 & 1800 & -106 \\
17 & 2000/08/12 & 0200 & 2000/08/13 & 1700 & -235 \\
18 & 2000/10/13 & 0200 & 2000/10/14 & 2300 & -107 \\
19 & 2000/10/28 & 2000 & 2000/10/29 & 2000 & -127 \\
20 & 2000/11/06 & 1300 & 2000/11/07 & 1800 & -159 \\
21 & 2000/11/28 & 1800 & 2000/11/29 & 2300 & -119 \\
22 & 2001/03/19 & 1500 & 2001/03/21 & 2300 & -149 \\
23 & 2001/03/31 & 0400 & 2001/04/01 & 2100 & -387 \\
24 & 2001/04/11 & 1600 & 2001/04/13 & 0700 & -271 \\
25 & 2001/04/18 & 0100 & 2001/04/18 & 1300 & -114 \\
26 & 2001/04/22 & 0200 & 2001/04/23 & 1500 & -102 \\
27 & 2001/08/17 & 1600 & 2001/08/18 & 1600 & -105 \\
28 & 2001/09/30 & 2300 & 2001/10/02 & 0000 & -148 \\
29 & 2001/10/21 & 1700 & 2001/10/24 & 1100 & -187 \\
30 & 2001/10/28 & 0300 & 2001/10/29 & 2200 & -157 \\
31 & 2002/03/23 & 1400 & 2002/03/25 & 0500 & -100 \\
32 & 2002/04/17 & 1100 & 2002/04/19 & 0200 & -127 \\
33 & 2002/04/19 & 0900 & 2002/04/21 & 0600 & -149 \\
34 & 2002/05/11 & 1000 & 2002/05/12 & 1600 & -110 \\
35 & 2002/05/23 & 1200 & 2002/05/24 & 2300 & -109 \\
36 & 2002/08/01 & 2300 & 2002/08/02 & 0900 & -102 \\
37 & 2002/09/04 & 0100 & 2002/09/05 & 0000 & -109 \\
38 & 2002/09/07 & 1400 & 2002/09/08 & 2000 & -181 \\
39 & 2002/10/01 & 0600 & 2002/10/03 & 0800 & -176 \\
40 & 2002/10/03 & 1000 & 2002/10/04 & 1800 & -146 \\
41 & 2002/11/20 & 1600 & 2002/11/22 & 0600 & -128 \\
42 & 2003/05/29 & 2000 & 2003/05/30 & 1000 & -144 \\
43 & 2003/06/17 & 1900 & 2003/06/19 & 0300 & -141 \\
44 & 2003/07/11 & 1500 & 2003/07/12 & 1600 & -105 \\
45 & 2003/08/17 & 1800 & 2003/08/19 & 1100 & -148 \\
46 & 2003/11/20 & 1200 & 2003/11/22 & 0000 & -422 \\
47 & 2004/01/22 & 0300 & 2004/01/24 & 0000 & -149 \\
48 & 2004/02/11 & 1000 & 2004/02/12 & 0000 & -105 \\
49 & 2004/04/03 & 1400 & 2004/04/04 & 0800 & -112 \\
50 & 2004/07/22 & 2000 & 2004/07/23 & 2000 & -101 \\
51 & 2004/07/24 & 2100 & 2004/07/26 & 1700 & -148 \\
52 & 2004/07/26 & 2200 & 2004/07/30 & 0500 & -197 \\
53 & 2004/08/30 & 0500 & 2004/08/31 & 2100 & -126 \\
54 & 2004/11/07 & 2100 & 2004/11/08 & 2100 & -373 \\
55 & 2004/11/09 & 1100 & 2004/11/11 & 0900 & -289 \\
56 & 2004/11/11 & 2200 & 2004/11/13 & 1300 & -109 \\
57 & 2005/01/21 & 1800 & 2005/01/23 & 0500 & -105 \\
58 & 2005/05/07 & 2000 & 2005/05/09 & 1000 & -127 \\
59 & 2005/05/29 & 2200 & 2005/05/31 & 0800 & -138 \\
60 & 2005/06/12 & 1700 & 2005/06/13 & 1900 & -106 \\
61 & 2005/08/31 & 1200 & 2005/09/01 & 1200 & -131 \\
62 & 2006/04/13 & 2000 & 2006/04/14 & 2300 & -111 \\
63 & 2006/12/14 & 2100 & 2006/12/16 & 0300 & -147 \\ \hline
\end{tabular}%
\end{table}

>>>>

%Local neurofuzzy modelling and singular spectrum analysis.
Apart from the NARMAX and neural network approaches, fuzzy methods have also been applied for $Dst$ prediction, \citet{SWE:SWE146} and \citet{Sharifi2006} outline the application of \emph{Local Neurofuzzy} models for one hour and two hour predictions of $Dst$ respectively. Local neuro-fuzzy models reduce the input space into a number of regions each with its own expert predictor. The combined model predicts $Dst$ for a new point as a linear combinations of the predictions from each expert weighted by a fuzzy score signifying the importance of each model for the provided input. For improving predictive performance of two hour $Dst$ forecasts in \citet{Sharifi2006}, the authors use \emph{singular spectrum analysis} (SSA). Singular spectrum analysis consists of extracting orthogonal components from a lagged time series, it is equivalent to \emph{principal component analysis} (PCA) which is quite extensively used in the machine learning community. \citet{loskutov2001testing} and \citet{loskutov2001study} provide a good background to the theory and application of SSA to geomagnetic time series.

%Talk about need for probabilistic forecasts.
Although much research has been done on prediction of the $Dst$ index, much less has been done on probabilistic forecasting of $Dst$. One such work described in \citet{McPherron:2013} involves identification of high speed solar wind streams using the WSA model (see \citet{WSAModel}), using predictions of high speed streams to construct ensembles of $Dst$ trajectories which yield the quartiles of $Dst$ time series.

A simple way to construct error bars on the predictions of forecasting models is by using the so called \textit{past cast} performance i.e. by calculating the standard deviations of the predictions generated by the model on a hold out data set. One limitation of such an approach is that the variance of the model predictions, once computed, remains static and does not adapt according to the inputs provided to the model. This may lead to overestimation or underestimation of the uncertainty around a models predictions depending on the prevelant geo-magnetic conditions and the data set used to calculate the \textit{past cast} model performance.

@@

From the validation results, we choose the model order which yields the best RMSE performance, for GP-AR it is $p_t = 6$ while for GP-ARX it is $p = 6, p_v = 1, p_b = 3$.

@@

\begin{table}[h]
\fontsize{9}{10.4}\selectfont
\centering
\caption{Storm events used to evaluate GP-AR and GP-ARX models}
\label{table:teststorms}
\begin{tabular}{cccccc}
\hline
Event Id & Start Date & Start Time & End Date & End Time & min. Dst \\ \hline
1 & 1998/02/17 & 1200 & 1998/02/18 & 1000 & -100 \\
2 & 1998/03/10 & 1100 & 1998/03/11 & 1800 & -116 \\
3 & 1998/05/04 & 0200 & 1998/05/05 & 0200 & -205 \\
4 & 1998/08/26 & 1000 & 1998/08/29 & 0700 & -155 \\
5 & 1998/09/25 & 0100 & 1998/09/26 & 0000 & -207 \\
6 & 1998/10/19 & 0500 & 1998/10/20 & 0800 & -112 \\
7 & 1998/11/09 & 0300 & 1998/11/10 & 1600 & -142 \\
8 & 1998/11/13 & 0000 & 1998/11/15 & 0400 & -131 \\
9 & 1999/01/13 & 1600 & 1999/01/14 & 2000 & -112 \\
10 & 1999/02/18 & 0300 & 1999/02/19 & 2100 & -123 \\
11 & 1999/09/22 & 2000 & 1999/09/23 & 2300 & -173 \\
12 & 1999/10/22 & 0000 & 1999/10/23 & 1400 & -237 \\
13 & 2000/02/12 & 0500 & 2000/02/13 & 1500 & -133 \\
14 & 2000/04/06 & 1700 & 2000/04/08 & 0900 & -288 \\
15 & 2000/05/24 & 0100 & 2000/05/25 & 2000 & -147 \\
16 & 2000/08/10 & 2000 & 2000/08/11 & 1800 & -230 \\
17 & 2000/08/12 & 0200 & 2000/08/13 & 1700 & -235 \\
18 & 2000/10/13 & 0200 & 2000/10/14 & 2300 & -107 \\
19 & 2000/10/28 & 2000 & 2000/10/29 & 2000 & -127 \\
20 & 2000/11/06 & 1300 & 2000/11/07 & 1800 & -159 \\
21 & 2000/11/28 & 1800 & 2000/11/29 & 2300 & -119 \\
22 & 2001/03/19 & 1500 & 2001/03/21 & 2300 & -149 \\
23 & 2001/03/31 & 0400 & 2001/04/01 & 2100 & -387 \\
24 & 2001/04/11 & 1600 & 2001/04/13 & 0700 & -271 \\
25 & 2001/04/18 & 0100 & 2001/04/18 & 1300 & -114 \\
26 & 2001/04/22 & 0200 & 2001/04/23 & 1500 & -102 \\
27 & 2001/08/17 & 1600 & 2001/08/18 & 1600 & -105 \\
28 & 2001/09/30 & 2300 & 2001/10/02 & 0000 & -148 \\
29 & 2001/10/21 & 1700 & 2001/10/24 & 1100 & -187 \\
30 & 2001/10/28 & 0300 & 2001/10/29 & 2200 & -157 \\
31 & 2002/03/23 & 1400 & 2002/03/25 & 0500 & -100 \\
32 & 2002/04/17 & 1100 & 2002/04/19 & 0200 & -127 \\
33 & 2002/04/19 & 0900 & 2002/04/21 & 0600 & -149 \\
34 & 2002/05/11 & 1000 & 2002/05/12 & 1600 & -110 \\
35 & 2002/05/23 & 1200 & 2002/05/24 & 2300 & -109 \\
36 & 2002/08/01 & 2300 & 2002/08/02 & 0900 & -102 \\
37 & 2002/09/04 & 0100 & 2002/09/05 & 0000 & -109 \\
38 & 2002/09/07 & 1400 & 2002/09/08 & 2000 & -181 \\
39 & 2002/10/01 & 0600 & 2002/10/03 & 0800 & -176 \\
40 & 2002/10/03 & 1000 & 2002/10/04 & 1800 & -146 \\
41 & 2002/11/20 & 1600 & 2002/11/22 & 0600 & -128 \\
42 & 2003/05/29 & 2000 & 2003/05/30 & 1000 & -144 \\
43 & 2003/06/17 & 1900 & 2003/06/19 & 0300 & -141 \\
44 & 2003/07/11 & 1500 & 2003/07/12 & 1600 & -105 \\
45 & 2003/08/17 & 1800 & 2003/08/19 & 1100 & -148 \\
46 & 2003/11/20 & 1200 & 2003/11/22 & 0000 & -422 \\
47 & 2004/01/22 & 0300 & 2004/01/24 & 0000 & -149 \\
48 & 2004/02/11 & 1000 & 2004/02/12 & 0000 & -105 \\
49 & 2004/04/03 & 1400 & 2004/04/04 & 0800 & -112 \\
50 & 2004/07/22 & 2000 & 2004/07/23 & 2000 & -101 \\
51 & 2004/07/24 & 2100 & 2004/07/26 & 1700 & -148 \\
52 & 2004/07/26 & 2200 & 2004/07/30 & 0500 & -197 \\
53 & 2004/08/30 & 0500 & 2004/08/31 & 2100 & -126 \\
54 & 2004/11/07 & 2100 & 2004/11/08 & 2100 & -373 \\
55 & 2004/11/09 & 1100 & 2004/11/11 & 0900 & -289 \\
56 & 2004/11/11 & 2200 & 2004/11/13 & 1300 & -109 \\
57 & 2005/01/21 & 1800 & 2005/01/23 & 0500 & -105 \\
58 & 2005/05/07 & 2000 & 2005/05/09 & 1000 & -127 \\
59 & 2005/05/29 & 2200 & 2005/05/31 & 0800 & -138 \\
60 & 2005/06/12 & 1700 & 2005/06/13 & 1900 & -106 \\
61 & 2005/08/31 & 1200 & 2005/09/01 & 1200 & -131 \\
62 & 2006/04/13 & 2000 & 2006/04/14 & 2300 & -111 \\
63 & 2006/12/14 & 2100 & 2006/12/16 & 0300 & -147 \\ \hline
\end{tabular}%
\end{table}
